# Proposal

## Research topic

We chose "NYC crimes" as our topic, because, as a resident of New York City, we would like to utilize the result of our analysis to avoid dangerous situation as much as possible. Although crime data for other cities in the United State might be accessible, we rather focus on New York City in order not to go off the rails from the purpose.

In this project, we clarify the characteristics of crimes and victims at a single point (cross-sectional) as well as time series trends. Specifically, we answer these questions below:

-   what type of crimes occur the most/least;

-   where crimes occur the most/least;

-   what type of people are likely to be victims;

-   do the characteristics above differ depending on the time the incident occurs;

-   is there any trends or changes in terms of time series.

Answering these questions will help us be safe, knowing how I am likely to be at risk and avoiding dangerous places and times. 

## Data availability
In order to find appropriate answers for our research questions, we choose "NYPD Complaint Data Current(Year To Date)" dataset from NYC Open Data website as our main data source to analyze. The URL of this dataset is https://data.cityofnewyork.us/Public-Safety/NYPD-Complaint-Data-Current-Year-To-Date-/5uac-w243 . This dataset contains all valid felony, misdemeanor and violation crimes reported to the New York City Police Department(NYPD), which demonstrates the reliability and authority of the data. The dataset is in CSV file format and it is updated by NYPD quarterly. So far, this dataset collects consecutive records starting from 1972 to 2022, which allow us to investigate changes of total number of crime reports with time and proportion of different types of crimes in each year. 

One crucial reason why we select this data source is that NYPD provides numerous accurate reports with detailed and various descriptions. The raw dataset contains approximately 400,000 crime records with 36 variable categories in total. There are many descriptive variables such as exact date of occurrence for the reported event, level of offense including felony, misdemeanor and violation, description of offense, suspect’s age and race group, etc. Supported by these variables of each observation, we can select and analyze data and illustrative information related to our research questions. For example, we need to filter out level of offense as well as description of offense categories in answering question “what type of crimes occur the most/least in NYC”. 

Nevertheless, there are some unimportant variables for our research questions. For example, the exact time of occurrence for the reported event time within a particular day, the name of the patrol borough in which the crime incident occurred and precise physical coordinates of location where reported event occurred. Further, it contains many null/NA values for many observations and unknown values for some observations. For instance, the age and race of suspect could be “unknown” in the dataset. Therefore, we need to remove unnecessary variables and modify the null values in data cleaning process.

The Socrata Open Data API (SODA) provides programmatic access to this data set including the ability to filter, query, and aggregate data. To download the data in R, we can register an account on NYC Open Data to create an app_token and access the data with Socrata Open Data API, which is a package called RSocrata in R. Once we download the dataset, we can save it locally and load it every time we analyze the data.

```{r download data, include = FALSE}
# install.packages("RSocrata")
# Download Data with:
library("RSocrata")
# df <- read.socrata(
  # "https://data.cityofnewyork.us/resource/5uac-w243.json",
  # app_token = "****",
  # email     = "****",
  # password  = "****"
  #)
# For safety reason, the app_token, email and password are concealed.

```



```{r save data}
## save dataset in local fold
# save(df,file="./dataset/rawdata.Rda")

## load local dataset
load("./dataset/rawdata.Rda")
```

## Data format
```{r data format}
colname <- c('CMPLNT_NUM', 'ADDR_PCT_CD', 'BORO_NM', 'CMPLNT_FR_DT', 'CMPLNT_FR_TM', 'CMPLNT_TO_DT', 'CMPLNT_TO_TM', 'CRM_ATPT_CPTD_CD', 'HADEVELOPT', 'HOUSING_PSA', 'JURISDICTION_CODE', 'JURIS_DESC', 'KY_CD', 'LAW_CAT_CD', 'LOC_OF_OCCUR_DESC', 'OFNS_DESC', 'PARKS_NM', 'PATROL_BORO', 'PD_CD', 'PD_DESC', 'PREM_TYP_DESC', 'RPT_DT', 'STATION_NAME', 'SUSP_AGE_GROUP', 'SUSP_RACE', 'SUSP_SEX', 'TRANSIT_DISTRICT', 'VIC_AGE_GROUP', 'VIC_RACE', 'VIC_SEX', 'X_COORD_CD', 'Y_COORD_CD', 'Latitude', 'Longitude', 'Lat_Lon', 'New Georeferenced Column')
description = c('Randomly generated persistent ID for each complaint', 'The precinct in which the incident occurred', 'The name of the borough in which the incident occurred', 'Exact date of occurrence for the reported event (or starting date of occurrence, if CMPLNT_TO_DT exists)', 'Exact time of occurrence for the reported event (or starting time of occurrence, if CMPLNT_TO_TM exists)', 'Ending date of occurrence for the reported event, if exact time of occurrence is unknown', 'Ending time of occurrence for the reported event, if exact time of occurrence is unknown', 'Indicator of whether crime was successfully completed or attempted, but failed or was interrupted prematurely', 'Name of NYCHA housing development of occurrence, if applicable', 'Development Level Code', 'Jurisdiction responsible for incident. Either internal, like Police(0), Transit(1), and Housing(2); or external(3), like Correction, Port Authority, etc.', 'Description of the jurisdiction code', 'Three digit offense classification code', 'Level of offense: felony, misdemeanor, violation', 'Specific location of occurrence in or around the premises; inside, opposite of, front of, rear of', 'Description of offense corresponding with key code', 'Name of NYC park, playground or greenspace of occurrence, if applicable (state parks are not included)', 'The name of the patrol borough in which the incident occurred', 'Three digit internal classification code (more granular than Key Code)', 'Description of internal classification corresponding with PD code (more granular than Offense Description)', 'Specific description of premises; grocery store, residence, street, etc.', 'Date event was reported to police', 'Transit station name', 'Suspect’s Age Group', 'Suspect’s Race Description', 'Suspect’s Sex Description', 'Transit district in which the offense occurred.', 'Victim’s Age Group', 'Victim’s Race Description', 'Victim’s Sex Description', 'X-coordinate for New York State Plane Coordinate System, Long Island Zone, NAD 83, units feet (FIPS 3104)', 'Y-coordinate for New York State Plane Coordinate System, Long Island Zone, NAD 83, units feet (FIPS 3104)', 'Midblock Latitude coordinate for Global Coordinate System, WGS 1984, decimal degrees (EPSG 4326)', 'Midblock Longitude coordinate for Global Coordinate System, WGS 1984, decimal degrees (EPSG 4326)', '', '')
types = c('Plain Text', 'Number', 'Plain Text', 'Date & Time', 'Plain Text', 'Date & Time', 'Plain Text', 'Plain Text', 'Plain Text', 'Number', 'Number', 'Plain Text', 'Number', 'Plain Text', 'Plain Text', 'Plain Text', 'Plain Text', 'Plain Text', 'Number', 'Plain Text', 'Plain Text', 'Date & Time', 'Plain Text', 'Plain Text', 'Plain Text', 'Plain Text', 'Number', 'Plain Text', 'Plain Text', 'Plain Text', 'Number', 'Number', 'Number', 'Number', 'Location', 'Point')
m_format <- data.frame(colname, description, types)
knitr::kable(m_format)

apply(is.na.data.frame(df), 2, sum)


```

