+---
title: "create_json_data"
---

```{r}
library(tidyverse)
library(dplyr)
library(plyr)

load('./rawdata.Rda')
```

## Ceate a dataset for geographic visualization

First, we narrow down the period of dataset into the last 10 years because too old data seems not to be helpful to understand the recent information.
Next, We remove some redundant rows and create additional columns so that we can analyze more deeply.
we remove "UNKNOWN" data in "vic_race", "vic_sex" and "vic_age_group"; we summarize "ofns_desc_group" since the classification is in detail too much. 

```{r}
# data in the last 10 years (2013-2022)
df <- mutate(df, lat=latitude, lon=longitude)
df_10y <- filter(df, cmplnt_fr_dt >= "2013-01-01")
  
# data preparation
df_10y$lat <- as.numeric(df_10y$lat)
df_10y$lon <- as.numeric(df_10y$lon)

# remove UNKNOWN data
df_10y <- df_10y[(df_10y[, "vic_race"]!="UNKNOWN") & (df_10y[, "vic_race"]!="(null)"), ]
df_10y <- df_10y[(df_10y[, "vic_sex"]=="M") | (df_10y[, "vic_sex"]=="F"), ] 
df_10y <- df_10y[df_10y[, "vic_age_group"]!="UNKNOWN", ]
df_10y <- df_10y %>%
  mutate(vic_race_group = case_when(vic_race == "AMERICAN INDIAN/ALASKAN NATIVE" | vic_race == "BLACK HISPANIC" ~ "OTHERS",
                                      TRUE ~ vic_race
                                      )
          ) %>%
    mutate(ofns_desc_group = factor(case_when(ky_cd == "101" ~ "MURDER",
                                         ky_cd == "104" | ky_cd == "115" | ky_cd == "116" | ky_cd == "233"　~ "SEXUALCRIME",
                                         ky_cd == "105" | ky_cd == "107" | ky_cd == "109" | ky_cd == "110" | ky_cd == "232" | 
                                           ky_cd == "341" | ky_cd == "343" ~ "ROBBERY",
                                         ky_cd == "106" | ky_cd == "343" | ky_cd == "344" | ky_cd == "355" | ky_cd == "358" | 
                                           ky_cd == "359" | ky_cd == "361" ~ "ASSAULT",
                                         ky_cd == "112" | ky_cd == "340" ~ "FRAUD",
                                         ky_cd == "578" ~ "HARASSMENT",
                                         TRUE ~ "OTHERS"
                                        ), levels=c("MURDER", "ASSAULT", "ROBBERY", "SEXUALCRIME", "FRAUD", "HARASSMENT", "OTHERS")
                                    )
           ) %>%
    mutate("sexual_crime" = factor(ifelse(ofns_desc_group == "SEXUALCRIME", "SEXUALCRIME", "OTHERS")))　%>%
    mutate("columbia" = factor(ifelse(abs(lon+73.96)<0.01 & abs(lat-40.81)<0.01, "Columbia_Area", "Others"))) %>%
    mutate("occ_hour" = substr(cmplnt_fr_tm, 1, 2)) 

df_10y$occ_hour <- as.integer(df_10y$occ_hour)
df_10y <- df_10y %>% 
  mutate("occ_hour_group" = factor(case_when(occ_hour >= 6 & occ_hour <= 11 ~ "morning",
                                              occ_hour >= 12 & occ_hour <= 17 ~ "afternoon",
                                              occ_hour >= 18 ~ "evening",
                                              occ_hour <= 5 ~ "midnight"
                                            ), levels=c("morning", "afternoon", "evening", "midnight")
  ))

df_10y <- df_10y[(df_10y[, "vic_age_group"]=="<18") | 
                 (df_10y[, "vic_age_group"]=="18-24") | 
                 (df_10y[, "vic_age_group"]=="25-44") | 
                 (df_10y[, "vic_age_group"]=="45-64") | 
                 (df_10y[, "vic_age_group"]=="65+"), ]

df_10y <- df_10y %>%
      mutate("vic_age_18_24" = factor(ifelse(vic_age_group == "18-24", "18-24", "Others")))

df_10y <- df_10y[, c(2,3,4,5,12,13,15,18,26,27,28,39,40,41,42,43,44,45,46,47)]

# df_10y <- na.omit(df_10y) 
```



## Write and save the new dataset

```{r}

save(df_10y, file = "df_10y.rda")
```
